Observations

### 2020-05-01 exp_eth_val.Rmd
resetting maps

library(knitr)
library(ggplot2)
library(forcats)
library(reshape2)
library(tidyr)
library(dplyr)
library(reshape)
library(ggpubr)
library(magick)

@@

Fig: \ref{fig:squaret} Ethnic global segregation

<!--
```{r prep, fig.pos="h!", out.width="98%",fig.align='center',fig.show="hold", fig.cap="prep fig", echo=FALSE, include=FALSE }

pl_sq_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .5:.5, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_sq_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .8:.2, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

 ggsave("pl_sq_e20.png",pl_sq_e20)
 ggsave("pl_sq_m20.png",pl_sq_m20)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

img <-c(image_read("pl_sq_e20.png"),image_read("pl_sq_m20.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "square20.png", format = "png")

pl_sq_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .5:.5, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_sq_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .8:.2, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ggsave("pl_sq_e50.png",pl_sq_e50)
ggsave("pl_sq_m50.png",pl_sq_m50)

img <-c(image_read("pl_sq_e50.png"),image_read("pl_sq_m50.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "square50.png", format = "png")

pl_sq_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .5:.5, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_sq_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%  
  gather(key = square, value = Segra, eth_sq_bl,val_sq_bl,eth_sq_or,val_sq_or) %>% 
  mutate("segregation" = fct_relevel(fct_collapse(square,"ethnic segregation" = c("eth_sq_bl","eth_sq_or"), "value segregation" = c("val_sq_bl","val_sq_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(square, "squared majority" = c("eth_sq_bl","val_sq_bl"), "squared minority" = c("eth_sq_or","val_sq_or")),"majority")) %>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square population, Majority:Minority = .8:.2, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ggsave("pl_sq_e80.png",pl_sq_e80)
ggsave("pl_sq_m80.png",pl_sq_m80)

img <-c(image_read("pl_sq_e80.png"),image_read("pl_sq_m80.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "square80.png", format = "png")

# circle

pl_cl_e20 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 20) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .5:.5, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_cl_m20 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 20) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .8:.2, 20% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ggsave("pl_cl_e20.png",pl_cl_e20)
ggsave("pl_cl_m20.png",pl_cl_m20)

img <-c(image_read("pl_cl_e20.png"),image_read("pl_cl_m20.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "circle20.png", format = "png")

pl_cl_e50 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 50) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .5:.5, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_cl_m50 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 50) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .8:.2, 50% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ggsave("pl_cl_e50.png",pl_cl_e50)
ggsave("pl_cl_m50.png",pl_cl_m50)

img <-c(image_read("pl_cl_e50.png"),image_read("pl_cl_m50.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "circle50.png", format = "png")

pl_cl_e80 <- dataone %>% filter(step == 1000 & fraction_blue == 50 & circle_blue == 80) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .5:.5, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

pl_cl_m80 <- dataone %>% filter(step == 1000 & fraction_blue == 80 & circle_blue == 80) %>%   gather(key = circlec, value = Segrac, eth_cl_bl,val_cl_bl,eth_cl_or,val_cl_or) %>% mutate("segregation" = fct_relevel(fct_collapse(circlec,"ethnic segregation" = c("eth_cl_bl","eth_cl_or"), "value segregation" = c("val_cl_bl","val_cl_or")), "ethnic segregation"), "group" = fct_relevel(fct_collapse(circlec, "cirle majority" = c("eth_cl_bl","val_cl_bl"), "circle minority" = c("eth_cl_or","val_cl_or")),"majority"))%>%  
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segrac)) + geom_tile() + 
  facet_grid(circle_orange ~ group + segregation, labeller = labeller(circle_orange = circle_minority.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle population, Majority:Minority = .8:.2, 80% Majority Circle") + 
  theme_bw() +  theme(legend.position = "right", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0))

ggsave("pl_cl_e80.png",pl_cl_e80)
ggsave("pl_cl_m80.png",pl_cl_m80)

img <-c(image_read("pl_cl_e80.png"),image_read("pl_cl_m80.png"))
c <- image_append(img, stack = TRUE)
image_write(c, path = "circle80.png", format = "png")

```
-->

@@

 ggsave("mn_e80.png",mn_e80)
 ggsave("mn_m80.png",mn_m80)
# a <- image_read("pl_sq_e20.png")
# b <- image_read("pl_sq_m20.png")

@@

# Global Results

Global results with heatmap

@@

glb <- annotate_figure(ggarrange(eth_eq , ggarrange(val_eq), nrow = 2), top = text_grob("Global Segregation, Local:Minority = 0.5:0.5",face = "bold", size = 12))

glb
```

@@

maj_val <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
 scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)
maj_val

maj_glb <- annotate_figure(ggarrange(maj_eth , ggarrange(maj_val), nrow = 2), top = text_grob("Global Segregation, Local:Minority = 0.8:0.2",face = "bold", size = 12))
maj_glb
```

>>>>

library(knitr)
library(ggplot2)
library(forcats)
library(reshape2)
library(tidyr)
library(dplyr)
library(reshape)
library(ggpubr)
library(magick)
library(gridExtra)
library(grid)

@@

@@

 ggsave("mn_e80.png",mn_e80)
 ggsave("mn_m80.png",mn_m80)
# a <- image_r
#knitr::include_graphics(c("pl_sq_e20.png","pl_sq_m20.png"))

@@

# Recap

- Research question: How the interplay of ethnic and value homophily preferences can explain difference in the degree of integration for the members of the same ethnic group (hybrid segregation) for both ethnic and value segregation.
- Focus: different weight on the two dimensions, heterogeneity among agents, relative group size for both dimensions \par

Utility of agents in Schelling relocation

$$
U= \beta_eX_v + \beta_vX_v + \epsilon
$$

```{r thheory, fig.pos="h", out.width="50%",out.width='\\textwidth',fig.align='left',fig.show="hold", fig.cap="Agents distinction and utility function", echo=FALSE, include=TRUE }

knitr::include_graphics("recapp.png")
```

# First Section (effect of relative group size)

* Aim:
    + Effect of different homophily preferences: independent effect of $\beta_e$ on ethnic segregation, and direct effect of beta value $\beta_v$ on value segregation.

Table \ref{tab:first}

\begin{table}[H]
\begin{tabular}{llll}
\midrule
 Static agent variable                      & Range         &      &                \\ \midrule
 Ethnicity  (\textit{color})         & Blue, Orange        \\
 Value orientation (\textit{shape}) & Square, Circle &  &  \\
 \midrule

 Parameters kept constant    & Slider & Range   & Experiments  \\ 
 \midrule
 Population density    & density                 & $[0,0.99]$   & $0.7$          \\
 Peak ethnic utility & similar\_wanted\_ethnic & $[0,1]$ & $1$ (linear function) \\
 Peak value utility & similar\_wanted\_value & $[0,1]$ & $1$ (linear function) \\
 \midrule
 Parameters modified in experiment & Slider  & Range   & Experiments  \\ 
 \midrule
 Ethnic group ratio (local\/minority)  & fraction\_blue &  $[0,1]$      & $0.5,0.8$  \\
 value ratio  blue population & circle\_blue & $[0,1]$      & $0.20,0.5,0.8$  \\
 value ratio  orange population & circle\_blue & $[0,1]$      & $0.20,0.5,0.8$  \\
 Determinism ethnic utility ($\beta_e$) & beta-ie for all agents & $[0,1]$ & $[0,10]$  \\
 Determinism value utility ($\beta_v$) & beta-iv for all agents & $[0,1]$ & $[0,10]$ \\
 \midrule
 Global output measures    & Computation &   Range & \\ 
 \midrule
 Ethnic segregation  & same color neighborhood proportion & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
 Value segregation  & same shape neighborhood proportion & $0,\stackrel{+0.1}{\dots}, 1$ & global and subgroups\\
   \midrule
\end{tabular}
\label{tab:first}
 \caption{Basic Model}

\end{table}

@@

glb <- annotate_figure(ggarrange(eth_eq , ggarrange(val_eq), nrow = 2), top = text_grob("Global Segregation, Majority:Minority = 0.5:0.5",face = "bold", size = 12))

glb

@@

maj_val <- ggplot(data=subset(dataone,fraction_blue == 80 & step == 1000), aes( beta_ie, beta_iv,fill= val_seg)) + geom_tile() +   facet_grid(circle_orange  ~  circle_blue,  space = "free_x", labeller = labeller(circle_blue = circle_local.labs,  circle_orange = circle_minority.labs )) + 
  scale_fill_distiller(name = "VALUE",palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) + 
 scale_x_discrete(name = "ß ethnic", limits=seq(0,10 ,by = 1)) + 
  scale_y_discrete(name = "ß value", limits=c(0,3,5,7,10))  + 
  theme_bw() + theme(strip.text.x = element_text(), legend.position = "right", panel.grid.minor.x = element_blank(), plot.title=element_blank(),  legend.margin=margin(0,0,0,0)) +
  geom_rect(data=subset(dataone,fraction_blue == 80 & step == 1000 & circle_orange == 50 & circle_blue == 50),aes(xmin = -1,xmax = 12, ymin = -1, ymax = 11),colour="black",size =2,alpha = 0)

maj_glb <- annotate_figure(ggarrange(maj_eth , ggarrange(maj_val), nrow = 2), top = text_grob("Global Segregation, Majority:Minority = 0.8:0.2",face = "bold", size = 12))
maj_glb

```{r sqro, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }

 circle_local.labs <- c("20% Circle \nMajority", "50% Circle \nMajority","80% Circle \nMajority")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Circle \nMinority", "50% Circle \nMinority","80% Circle \nMinority")
names(circle_minority.labs) <- c("20", "50","80")

sqroeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_or","Ethnic" = "eth_sq_or"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square orange, ethnic minority") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )

sqromj<- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_sq_or,val_sq_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_or","Ethnic" = "eth_sq_or"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square orange, ethnic minority") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )

#grid.arrange(grob(sqroeq),grob(sqromj), ncol =  1, common.legend = TRUE,legend = "bottom")

 sqroeq
 sqromj
```

```{r crloA, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }

dataone$rev_circle_orange <- fct_rev(factor(dataone$circle_orange))

 circle_blue.labs <- c("20% Circle Blue", "50% Circle Blue","80% Circle Blue")
names(circle_blue.labs) <- c("20", "50","80")
 rev_circle_orange.labs <-  c("80% Circle \nOrange", "50% Circle \nOrange","20% Circle \nOrange")
names(rev_circle_orange.labs) <- c("80", "50","20")

crloeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(rev_circle_orange ~ circle_blue + segregation, labeller = labeller(rev_circle_orange = rev_circle_orange.labs, circle_blue = circle_blue.labs), switch  = "y") +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5), position = "right") +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle orange, equal ethnic size") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
 crloeq

crlomj <- dataone %>%  filter(fraction_blue == 80) %>%  gather(key = subgroup, value = Segra, eth_cl_or,val_cl_or) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_cl_or","Ethnic" = "eth_cl_or"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Circle orange, ethnic minority") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )

#grid.arrange(grob(sqroeq),grob(sqromj), ncol =  1, common.legend = TRUE,legend = "bottom")

 crloeq
 crlomj
```

```{r sqrb, fig.pos="t",out.width='\\textwidth',fig.show = "hold",fig.pos='t',fig.align='center',fig.show="hold", fig.cap="", echo=FALSE, include=TRUE  }

 circle_local.labs <- c("20% Circle \nMajority", "50% Circle \nMajority","80% Circle \nMajority")
names(circle_local.labs) <- c("20", "50","80")
 circle_minority.labs <-  c("20% Circle \nMinority", "50% Circle \nMinority","80% Circle \nMinority")
names(circle_minority.labs) <- c("20", "50","80")

sqrbeq <- dataone %>%  filter(fraction_blue == 50) %>%  gather(key = subgroup, value = Segra, eth_sq_bl,val_sq_bl) %>% mutate(`segregation` = fct_relevel(fct_collapse(subgroup,"Value" = "val_sq_bl","Ethnic" = "eth_sq_bl"), "Value"))  %>% 
  ggplot(aes(x = beta_ie,y = beta_iv, fill = Segra)) + geom_tile() + 
  facet_grid(circle_orange ~ circle_blue + segregation, labeller = labeller(circle_orange = circle_minority.labs, circle_blue = circle_local.labs)) +
  scale_fill_distiller(palette = "RdBu", limits=c(0,1), breaks=c(0,0.2,0.5,0.8,1)) +
  scale_x_discrete( limits=c(0,10, by = 5)) +
  scale_y_discrete( limits=c(0,10, by = 5)) +
  xlab("ß ethnic") + ylab("ß value") + ggtitle("Square blue, equal ethnic size") + 
  theme_bw() +  theme(legend.position = "bottom", legend.title = element_blank(), panel.grid.minor.x = element_blank(), plot.title=element_text(hjust = 0.5),  legend.margin=margin(0,0,0,0), 
                      panel.spacing.x  = unit(0.2, "lines"),panel.spacing.y  = unit(0.1, "lines") )
